The Analysis of Pluralistic Ignorance of Married Men in Saudi Arabia on Women Working Outside of Home (WWOH) ^[Code and data are available at: https://github.com/YcartXin/Analysis-of-Men-in-Saudi-Arabia-on-WWOH]

### 2024-02-15 paper/paper.qmd
Added more tables, graphs, citations.

#install.packages("tidyverse")
#install.packages("here")
#install.packages("knitr")

@@

```{r}
#| echo: false
#| label: fig-wwoh
#| fig-cap: Support of Young Married Men in Saudi Arabia of WWOH
online_cleaned |> 
  ggplot(aes(x = c_outside_self)) +
  geom_bar() +
  theme_minimal() +
  labs(x = "Support of WWOH (Y = 1/N = 0)", y = "Frequency of Responses" )

@@

```{r}
#| echo: false
#| label: fig-time
#| fig-cap: Density Histogram of Percentage Wedge
histogram <- main_cleaned |>
  mutate(percentage_wedge = outside_wedge/30*100)

p <- ggplot(histogram, aes(x = percentage_wedge)) + 
  geom_histogram(aes(y = after_stat(density)), binwidth = 8, fill = "green", alpha = 0.6, color = "black") + 
  labs(
       x = "Percentage Wedge Value",
       y = "Density") + 
  theme_minimal() +
  theme(plot.caption = element_text(hjust = 0, face = "italic", size = 10),
        plot.caption.position = "plot") +
  scale_x_continuous(limits = c(-100, 100))

print(p)
```
In @fig-time, from assessing the distribution of these wedges throughout all sessions, the data revealed that a substantial majority (72%) of the participants consistently undervalue the level of endorsement for WWOH within their session cohorts. On average, this wedge is observed to be a 24 percentage points difference, aligning very similarly with the conclusions drawn from the original paper @paper. Thus, the second claim of that married men massively underestimate the level of support from other men in their communities is further substantiated.

@@

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

@@

\appendix

# Appendix {-}

## Diagnostics

>>>>

#install.packages("tidyverse")
#install.packages("here")
#install.packages("knitr")
#install.packages("kableExtra")
#install.packages("webshot")

@@

```{r}
#| echo: false
#| label: fig-wwoh
#| fig-cap: Support of Young Married Men in Saudi Arabia of WWOH

online_cleaned |> 
  ggplot(aes(x = c_outside_self)) +
  geom_bar() +
  theme_minimal() +
  labs(x = "Support of WWOH (Y = 1/N = 0)", y = "Frequency of Responses" )

@@

```{r}
#| echo: false
#| label: fig-time
#| fig-cap: Density Histogram of Percentage Wedge on Difference Between Beliefs and Actual Calculation
histogram <- main_cleaned |>
  mutate(percentage_wedge = outside_wedge/30*100)

p <- ggplot(histogram, aes(x = percentage_wedge)) + 
  geom_histogram(aes(y = after_stat(density)), binwidth = 8, fill = "green", alpha = 0.6, color = "black") + 
  labs(
    x = "Percentage Wedge Value",
    y = "Density") + 
  theme_minimal() +
  theme(plot.caption = element_text(hjust = 0, face = "italic", size = 10),
        plot.caption.position = "plot") +
  scale_x_continuous(limits = c(-100, 100))
print(p)

In @fig-time, from assessing the distribution of these wedges throughout all sessions, the data revealed that a substantial majority (72%) of the participants consistently undervalue the level of endorsement for WWOH within their session cohorts. On average, this wedge is observed to be a 24 percentage points difference, aligning very similarly with the conclusions drawn from the original paper @paper. Thus, the second claim of that married men massively underestimate the level of support from other men in their communities is further substantiated.

The last claim this replication paper is going to focus on is that correcting beliefs about others' feelings will affect the outcome of whether the married man's wife works. In the main experiment done by Bursztyn et.al, a follow up survey three months later records the difference in the participant's wife's employment difference @paper. As the men experienced learning about others' surprisingly supportive views on WWOH during the first survey, this three-month difference in wifes' employments maybe attributed to the correcting of beliefs. The difference is shown in  below.

```{r}
#| echo: false
#| label: tbl-empl
#| tbl-cap: Employment Difference of Wives between Two Surveys Three Months Apart
#| tbl-subcap: ["Treatment", "Control"]
#| layout-ncol: 2

follow_cleaned |> filter(condition2==1) |>
  count(emply_prev, emply_now) |> kable()

follow_cleaned |> filter(condition2==0) |>
  count(emply_prev, emply_now) |> kable()

```
As seen in @tbl-empl, there are slight differences between the treatment and control group in terms of the participants' wives employment since the first survey.

@@

```{r}
#| echo: false
#| label: fig-diss
#| fig-cap: Frequency of WWOH Discussions for Participants in Survey

chart <- sec_cleaned |>
  mutate(freq = case_when(
    discuss_freq == 1 ~ "Very Often",
    discuss_freq == 2 ~ "Often",
    discuss_freq == 3 ~ "Sometimes",
    discuss_freq == 4 ~ "Rarely",
    discuss_freq == 5 ~ "Very Rarely"))

chart |>
  ggplot(mapping = aes(x = freq)) +
  geom_bar() +
  theme_minimal() +
  labs(x = "Age group", y = "Number of observations")

@@
